```{r, include = FALSE}
tables <- readRDS("results/tables/descriptives_all_tables.rds")
```

# Appendix 

## Regression model for the fairness rankings

We used a rank-ordered logit model [@hausman1987specifying] to estimate the effect of a change in the expected number of asylum seekers under a relocation scheme on the probability of ranking the scheme higher in the fairness ranking. This model allows probabilities to depend on the differences among all alternatives in a latent "fairness" variable. We assume the latent variable to be a function of the expected asylum seekers (scaled), $AS$, and we allow the coefficients to vary by treatment. This can be formulated as:
\[
    \mu_{ijt} = \alpha_{jt} + \beta_{jt} \text{AS},
\]
for all $i$ and $j$ alternatives, with $\beta_{jt}$ set to zero for an arbitrary alternative and an arbitrary treatment condition. We selected the no-relocation scheme as the reference alternative, and the reference treatment group is the absolute-information group, so the model yields estimates of differences between control vs absolute and absolute vs relative information.


## Questionnaire

TBA

## Additional Tables

```{r assignment-summary}
tables$raw$tbl_assignment |> 
    kableExtra::kbl(
        caption = "Random assignment of respondents, by country",
        format.args = list(big.mark = " "),
        booktabs = TRUE,
        linesep = c(rep("", 7), "\\addlinespace")
    ) |> 
    kableExtra::kable_styling(full_width = TRUE) |>
    kableExtra::column_spec(1, bold = TRUE)
```


```{r, eval = FALSE}
require(dplyr)
require(kableExtra)
tbl_relocation |>
    kbl(
        caption = "Expected asylum applications (per 100 000 locals) under no relocation, relocation by GDP, and relocation by population", 
        caption.short = "Expected asylum applications",
        booktabs = TRUE,
        linesep = "",
        toprule = "\\addlinespace[1em]\\toprule",
    ) |>
    kable_styling(
        full_width = TRUE,
        position = "center",
        latex_options = c("hold_position"),
        font_size = 12,
        stripe_color = "gray!10"
    ) |>
    column_spec(1, bold = TRUE)
```

