```{r methods, include = FALSE}
suppressMessages({
    library(dplyr)
    library(knitr)
    library(tidyr)
    library(stringr)
    library(kableExtra)
})
```

# Methods and Data

## The survey

A sample representative of the adult population aged 18 years and over in eight EU countries (Bulgaria, France, Germany, Greece, Italy, Poland, Spain and Sweden) was drawn from Ipsos online panel by means of stratified random probability sampling. The selected countries were chosen to ensure a balanced representation of the European Union's diversity, with particular attention to coverage across macro-regions (Northern, Southern, Eastern, and Western Europe). The selection also reflects variation in key structural characteristics, including economic conditions (GDP per capita), population size, and the share of foreign-born residents.

The sampling was stratified by age, gender and geographic region (NUTS 1). Pre-defined sub-sample sizes ("quotas") were based on official population statistics provided by Eurostat. The overall sample size of the project included 8,122 participants. The main fieldwork took place between 30 September 2024 and 21 October 2024. Details of the field work and survey design are available elsewhere [see @blasco2025fairness].

## Experimental design

The survey embededed an experiment testing how different types of information affected participants' ranking of the fairness of three relocation rules for asylum seekers across EU countries:^[
    The experimental design and pre-analysis plan were pre-registered within the AEA RCT Registry (AEARCTR-0014194). The Ethics Research Board of the JRC approved the experimental protocol.
]

- **No relocation** (the baseline): asylum seekers remain in the country where they first arrive;
- Allocation **proportional to each country's population**: relocations ensure equity with population as a proxy for capacity;
- Allocation **proportional to each country's GDP**: relocations ensure equity with GDP as a proxy for capacity.

Respondents were asked to rank these allocation rules from the fairest (rank = 1) to the least fair (rank = 3). Before they did so, we varied the format and amount of information available across three conditions: 

- **No information** (the control),
- **Absolute** information: the expected number of asylum applications under each relocation scheme (expressed in thousands),
- **Relative** information: the expected number of asylum applications under each relocation scheme per 100,000 citizens.

To illustrate the underlying relocation problem captured by our experiment, Table \@ref(tab:relocation) reports the expected asylum applications in each country under each relocation rule. These figures are based on national statistics about each country's population, GDP, and historical (2014-2023) first-time asylum applications from Eurostat.^[
    In this study, GDP and population are intended as proxies for a country's reception and processing capacity, consistent with existing EU allocation proposals and policy debates [@thielemann2018refugee]. These indicators also provide respondents with clear and easily interpretable signals of a country's size and wealth, which research shows are commonly used when evaluating fairness in international burden-sharing [@kleider2019politics]. Nevertheless, respondents may interpret proportionality by GDP or population as reflecting different underlying dimensions of capacity (e.g., economic resources, institutional capacity, housing availability, or labour market conditions). Likewise, respondents' rankings of the allocation principles may reflect judgments about both the fairness of the allocation mechanism and the fairness or desirability of its expected outcomes. These interpretive ambiguities should be borne in mind when interpreting the results.
]

A few observations can be made. First, historical asylum application rates vary substantially across countries, ranging from 16 per 100,000 inhabitants in Poland to 397 per 100,000 in Greece. Second, proportional allocation systems would significantly alter the current distribution of asylum applications. For example, under a population-proportional allocation scheme, Poland would receive an additional 153 applications per 100,000 inhabitants, while Greece would "send" 228 applications per 100,000 inhabitants to other countries. We refer to countries in this position as “net receivers” or “net senders.” Third, proportional allocation rules would generate pronounced cross-country differences depending on the rule being based on population or GDP. For instance, under a GDP-proportional allocation system, Poland would still be a net receiver, but the additional inflow would be considerably smaller, decreasing from 153 applications per 100,000 inhabitants under a population-based system to 76 per 100,000 under a GDP-based system.

```{r relocation, eval = is_html_or_latex()}
tab <- readRDS("../output/tables/table_asylum_relocation.rds")
tab |>
    kableExtra::kbl(
        caption = paste(
            "Expected asylum applications under alternative",
            "burden-sharing rules (per 100,000 inhabitants)."
        ),
        booktabs = TRUE,
        linesep = "",
        align = c("l", rep("r", 5)),
        escape = FALSE
    ) |>
    kableExtra::kable_styling(
        latex_options = c("hold_position"),
        full_width = FALSE,
        position = "center",
        font_size = 10
    ) |>
    kableExtra::row_spec(0, bold = TRUE) |>
    kableExtra::add_header_above(
        c(" " = 1, "Levels" = 3, "Differences vs. no relocation" = 2),
        bold = TRUE
    ) |>
    kableExtra::footnote(
        general = "Entries report expected asylum applications per 100,000 inhabitants.",
        threeparttable = TRUE,
        general_title = "Note:"
    )
```

Finally, the survey included several modules that asked respondents about their socio-demographics, perceptions of the EU asylum system, support for different migration policies, and other background questions. The full questionnaire is in the Appendix. A descriptive analysis of the responses is presented in the technical report by @blasco2025fairness. In our analysis, we included control variables such as trust or political affiliation, as these are associated with attitudes towards migration [e.g.,@canetti2016threatened;@mitchell2021social]. We also consider various socio-demographic factors, such as income and employment status, gender, age, and the parents' country of birth. Whether the respondent was born abroad may be relevant because foreigners may hold different opinions on migration issues than natives [@berlinschi2019migrants].

## Data 

Table \@ref(tab:random-assignment) shows that, within each country, the sample is split evenly across treatment groups, as expected under the stratified randomisation design.

Table \@ref(tab:summary) presents summary statistics and assesses covariate balance across the treatment groups for key pre-treatment characteristics, including sex, age, education, political opinions, and perceptions of the asylum system. On average, respondents were approximately 50 years old (with 16 years SD), with about half (47%) identifying as male. The sample was skewed toward more highly educated individuals, with approximately 40% of respondents reporting high educational attainment (ISCED 5–8), around 50% medium attainment (ISCED 3–4), and only 10% low attainment (ISCED 0–2). On measures of trust, respondents reported moderate levels of general trust in others (M = 4.5, SD = 2.7), trust in the EU (M = 4.3, SD = 2.7), and trust in government (M = 3.7, SD = 2.9). 

Respondents reported, on average, a basic knowledge of the EU asylum system, with a mean score of 2.0 (SD = 0.7) on a 1-4 scale (1 = no knowledge, 4 = expert knowledge). Most respondents perceived that there were "too many" asylum seekers in their country, with a mean of 2.6 on 1-3 scale (1 = too few and 3 = too many). Similarly, respondents generally viewed the distribution of asylum seekers across the EU as uneven, reporting an average score of 3.1 (SD = 2.4) on 0-10 scale measuring perceived evenness across the EU. Despite these perceptions, respondents expressed a broad support for burden sharing among countries, as well as for ensuring equal rights, equal treatment, and having an equal distribution of asylum seekers, with means ranging from 6.9 to 7.4 on 0-10 scales. 

We find no evidence of imbalance in the sample across the treatment groups. As shown in Table \@ref(tab:summary), the maximum standardised mean difference across groups was below 0.1 for all variables, indicating good covariate balance, as values greater than 0.1 are generally considered as evidence of imbalance.

```{r summary}
tab <- readRDS("../output/tables/covariate_balance.rds")
tab |>
    dplyr::select(
        variable,
        max_smd,
        estimate_Absolute,
        SD_Absolute,
        estimate_Control,
        SD_Control,
        estimate_Relative,
        SD_Relative,
    ) |>
    kableExtra::kbl(
        col.names = c("Variable", "SMD", rep(c("Mean", "SD"), 3)),
        booktabs = TRUE,
        digits = 1,
        caption = "Summary statistics and covariate balance across treatments."
    ) |>
    kableExtra::kable_classic(
        full_width = FALSE, 
        position = "center"
    ) |>
    kableExtra::row_spec(0, bold = TRUE) |>
    kableExtra::add_header_above(
        c(" " = 2, Absolute = 2, Control = 2, Relative = 2),
        bold = TRUE
    ) |>
    footnote(
        "SMD = standardized mean difference (max across groups); SD = standard deviation."
    )
```