```{r results, include = FALSE}
library(dplyr)
library(brms)
library(broom.mixed)
library(kableExtra)
library(ggplot2)
library(ggtext)

# data_dir <- file.path("data", "processed")

# tab_dir <- file.path("results", "tables")
# tables_rologit <- readRDS(file.path(tab_dir, "rologit_coeffs.rds"))
# tbl_coeffs_hetero_raw <- readRDS(file.path(tab_dir, "rologit_coeffs_hetero.rds"))

recode_labels <- function(df) {
    df %>%
        mutate(
            relocation = dplyr::replace_values(
                as.character(alt),
                "Relocation: by pop" ~ "Population",
                "Relocation: by GDP" ~ "GDP"
            ),
            relocation_treatment = dplyr::replace_values(
                as.character(treatment),
                "Info: Absolute" ~ "Absolute",
                "Info: Relative" ~ "Relative"
            )
        )
}

ds_long <- ds_long %>%
    left_join(
        tbl_asylum_rel,
        by = "country"
    ) %>%
    mutate(
        country_label = case_when(
            no_relocation > population ~ "Net sender",
            no_relocation < population ~ "Net receiver",
            TRUE ~ "Other"
        )
    ) %>% 
    recode_labels()
```

```{r, results = "asis"}
if (params$debug) {
    cat("\\clearpage")
}
```

# Results

## Perceived fairness of the relocation systems

Respondents ranked three relocation mechanisms according to perceived fairness. Overall, a large majority of respondents (over 74%) ranked proportional relocation mechanisms as the fairest option. In the no-information group, the GDP-based allocation received the highest share (39%), followed closely by population-based allocation (35%), with only 26% considering no relocation as the fairest option.^[
    A one-sample proportion test shows that this result is significantly lower (p<0.01) than the 33% expected if individuals were ranking alternatives at random or were indifferent among the options.
]

Figure \@ref(fig:toprank) displays the share selecting each mechanism as the fairest option, by information treatment and  by whether countries are net senders or net receivers. We observe a substantial variation across information treatments and country groups. 

Among net sender countries, only 13% and 17% of respondents in the absolute and relative information groups, respectively, selected "no relocation" as the fairest option, compared to 27% in the no-information group. Thus, information provision reduces the share favouring no relocation by about 10 percentage points. 

By contrast, among the net receiver countries, the corresponding shares are higher (34% and 28% in the absolute and relative condition, respectively), compared to 24% in the control group. Hence, information provision increases perception of fairness for no relocation by about 10 percentage points.

Since the information condition was randomly assigned, these patterns provide evidence of (1) a causal effect of information provision and (2) heterogeneous effects across country groups, with  effect changes direction across country groups, with directionally opposite responses consistent with self-serving bias.

```{r toprank, fig.cap = cap, out.width="\\textwidth"}
knitr::include_graphics(
    here::here("output", "figures", "top_rank_by_cntry_type.png"),
    auto_pdf = TRUE
)

cap <- "Share of respondents selecting each relocation mechanism as the most fair across information conditions: no information (control), relative information, and absolute information about asylum seekers under each regime. Countries are classified as net senders (receivers) when asylum applications per 100,000 inhabitants exceed (fall below) the proportional-by-population relocation relative to a no-relocation benchmark." # nolint
```

 Country-by-country analysis (Figure \@ref(fig:toprank-by-cntry) in the Appendix) shows a consistent pattern, with magnitude differences across countries. For instance, in Germany (a net receiver), 58% ranked some form of relocation as the fairest option, which is the lowest share among the selected countries, while in Greece (a net sender) the proportion was highest at 87%. Relocation by GDP was commonly perceived as the fairest in Bulgaria (53%), Greece (48%) and Spain (48%), but not in Germany (19%) or Sweden (27%). Views on relocation by population also varied: the share of respondents assigning it the top rank range from 24% in Poland to 45% in Italy. 

<!-- These stark differences suggest that country-specific conditions, such as the political climate, refugee situation, and socio-economic differences, play a significant role in shaping public perceptions of fairness. -->


## Average Treatment Effects on Fairness Rankings

Figure \@ref(fig:mean-rank) illustrates the expected fairness rankings of each relocation mechanism conditional on the information treatment and country type (net sender vs receiver), as estimated from linear regression. 

In net-receiving countries, including France, Italy, Poland, and Spain, respondents in the no-information condition perceived “no relocation” as the least fair option, with a mean rank of 2.4 out of 3. However, the perceived fairness of “no relocation” increases under both information conditions, with the largest effect observed in the absolute-information condition, where its mean rank improves from 2.4 to 2.1. By contrast, in net sender countries, such as Bulgaria, Germany, Greece, and Sweden, "no relocation" receives higher fairness rankings in the information treatments, increasing from 2.4 in the control to 2.6 in the absolute-information condition, indicating weaker perceived fairness.  Overall, these results show a strong effect of information provision, which confirms our hypotheses that individuals react more when information is presented in absolute than in relative terms.^[
    As a formal test of the overall associations between fairness rankings and treatment assignment, we used separate Chi-squared tests within each country with Bonferroni correction for multiple testing. Even after applying Bonferroni correction, all the country-specific associations were statistically significant (p. < 0.01), confirming a robust treatment effect in most countries, as hypothesised.
]

```{r mean-rank, fig.height = 4, fig.width = 7, fig.cap = cap}
p_avg_rank

cap <- paste(
    "Information provision and fairness rankings. Points show the expected fairness rankings (with 95\\% CI) conditional on the assigned information treatment and the country of residence being net sender or net receiver. Lower average ranks indicate higher perceived fairness. Countries are classified as net receivers if expected asylum applications are higher under relocation than under no relocation (based on GDP or population), and as net senders otherwise." # nolint
)
```

## The role of asylum seekers

We now examine how the expected number of asylum seekers influences perceived fairness across relocation schemes using linear regression. Figure \@ref(fig:m1-coeffs) presents the results from two model specifications. Model 1 assumes a constant effect of the expected asylum seekers for each alternative allocation scheme across, while Model 2 allows this effect to vary by the information treatment.^[
    Results are robust to a rank-ordered logit model for the probability of ranking each relocation scheme higher in the fairness ranking (see the Appendix).
]

Both models indicate a significant increase in fairness rankings when moving from any proportional allocation to No relocation, of approximately 0.4 points. Thus, no relocation is perceived as less fair, all else equal.

The models also consistently exhibit a self-serving bias: perceived fairness of each allocation mechanism decreases as the expected number of asylum applications increases. Specifically, a one-standard-deviation increase in expected applications raises the fairness ranking of the No relocation option by about 0.2 points, indicating that proportional allocation schemes are viewed as less fair when they entail more expected applications. 

However, when we allow the information treatment to vary with the expected number of applications, we find that the effect of asylum applications is almost entirely offset in the No information treatment and is smaller in the Relative information treatment than in the Absolute information treatment. Figure XXX illustrates the implications for expected fairness rankings. A proportional-by-population allocation with a high number of expected applications (250 per 100,000 inhabitants) is ranked significantly more fair under the Absolute information treatment than under No information. In contrast, a No relocation scheme with fewer expected applications (100 per 100,000 inhabitants) is perceived as significantly fairer under Absolute information than under No information.

```{r m1}
ds_m1  <- tbl_asylum_rel %>% 
    tidyr::pivot_longer(
        c("population", "gdp", "no_relocation"),
        names_to = "relocation",
        values_to = "asylum_applications"
    ) %>% 
    mutate(
        relocation = recode_values(
            relocation,
            "gdp" ~ "GDP",
            "population" ~ "Population",
            "no_relocation" ~ "No relocation"
        )
    ) %>% 
    right_join(
        dplyr::select(
            ds_long,
            rank, country, relocation, treatment = relocation_treatment,
            political_right
        ),
        by = c("relocation", "country")
    ) 

m1 <- brm(
    formula = rank ~ treatment *(relocation  + scale(asylum_applications)) + country,
    data = ds_m1,
    file = "m1.rds",
    file_refit = "on_change",
    cores = 4,
)

m1_baseline <- brm(
    formula = rank ~ treatment * relocation + scale(asylum_applications) + country,
    data = ds_m1,
    file = "m1_baseline.rds",
    file_refit = "on_change",
    cores = 4,
)
```

```{r m1-coeffs, fig.cap = cap, fig.width = 7, fig.height = 4}
cap <- paste(
    "Coefficient estimates from a linear regression predicting fairness rankings, showing fixed effects of the information treatment, relocation mechanism, asylum application levels (scaled), and their interactions (country fixed effects omitted). Points represent mean differences from the baseline (relocation by GDP under absolute information, with average asylum applications) and horizontal intervals indicate 95% intervals."
)

replace_terms <- function(x) {
    replace_values(
        x,
        "treatmentNoinfo" ~ "No info",
        "treatmentRelative" ~ "Relative info",
        "relocationNorelocation" ~ "No relocation",
        "relocationPopulation" ~ "Relocation by population",
        "scaleasylum_applications" ~ "Asylum applications (scaled)",
        "treatmentNoinfo:relocationNorelocation" ~ "No relocation x No info",
        "treatmentRelative:scaleasylum_applications" ~ "Relative x Asylum app. (scaled)",
        "treatmentNoinfo:scaleasylum_applications" ~ "No info x Asylum app. (scaled)",
        "treatmentRelative:relocationNorelocation" ~ "No relocation x Relative",
        "treatmentNoinfo:relocationPopulation" ~ "Reloc. by pop. x No info",
        "treatmentRelative:relocationPopulation" ~ "Reloc. by pop. x Relative"
    )
}

list(
    "Model 1" = tidy(m1_baseline),
    "Model 2" = tidy(m1)
) %>% 
    bind_rows(.id = "model") %>% 
    filter(
        effect == "fixed", 
        component == "cond",
        !grepl("country|Intercept", term)
    ) %>%
    mutate(
        group = case_when(
            grepl("asyl", term) ~ "Asylum\napplications",
            grepl("Popul", term) ~ "By population",
            grepl("Noreloc", term) ~ "No relocation",
            TRUE ~ ""
        )
    ) %>%
    ggplot(
        aes(
            x = estimate,
            y = replace_terms(term),
            xmin = conf.low,
            xmax = conf.high,
            color = model
        )
    ) + 
    facet_grid(group ~ ., scales = "free_y", space = "free", switch = "y") +
    geom_vline(xintercept = 0, color = "salmon") +
    ggdist::geom_pointinterval(
        position = position_dodge(.4)
    ) + 
    labs(
        color = "Model",
        x = "Fairness ranks differences (coeffs, 95% CIs)",
        y = NULL
    ) + 
    theme(
        strip.background = element_blank(),
        strip.placement = "outside",
    )
```

```{r m1-ce}
ce <- conditional_effects(
    m1,
    effects = "treatment:asylum_applications",
    conditions = data.frame(
        relocation = c("No relocation", "Population")
    )
)

ce <- conditional_effects(
    m1,
    effects = "relocation:asylum_applications",
    conditions = data.frame(
        treatment = c("No info", "Absolute")
    )
)

df <- ce[[1]]

p <- ggplot(df, aes(
    x = asylum_applications, #factor(treatment, c("No info", "Relative", "Absolute")),
    y = estimate__,
    ymin = lower__,
    ymax = upper__,
    group = treatment,
    color = treatment,
    shape = treatment
)) +
    facet_wrap (~ relocation) + 
    geom_point(
        size = 4,
        position = position_dodge(0.2)
    ) +
    geom_errorbar(
        position = position_dodge(0.2)
    ) +
    geom_ribbon(aes(ymin = lower__, ymax = upper__, fill = treatment),
        alpha = 0.2, color = NA,
        position = position_dodge(width = 0.2)
    ) +
    theme_classic(base_size = 14) +
    theme(
        panel.grid.major = element_line(color = "gray", linewidth = .1),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold"),
        axis.title = element_text(face = "bold"),
        axis.text = element_text(color = "black"),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    labs(
        x = "Asylum applications (per 100,000 inhabitants)",
        y = "Fairness rank (average)"
    ) +
    scale_color_brewer(palette = "Dark2") +
    scale_fill_brewer(palette = "Dark2")

p 
```


```{r m-political-right}
m_political_right <- brm(
    formula = rank ~ political_right * treatment *(relocation  + scale(asylum_applications)) + country,
    data = ds_m1,
    file = "m_political_right.rds",
    file_refit = "on_change",
    cores = 4,
)
```

```{r m-conditional}
ce <- conditional_effects(
    m_political_right,
    effects = "treatment:relocation",
    conditions = data.frame(
        asylum_applications = 320,
        political_right = seq(0, 10, by = 3)
    )
)
df <- ce[[1]]


p <- ggplot(df, aes(
    x = political_right, #factor(treatment, c("No info", "Relative", "Absolute")),
    y = estimate__,
    ymin = lower__,
    ymax = upper__,
    group = treatment,
    color = treatment,
    shape = treatment
)) +
    facet_wrap (~ relocation) + 
    geom_point(
        size = 4,
        position = position_dodge(0.2)
    ) +
    geom_errorbar(
        position = position_dodge(0.2)
    ) +
    geom_ribbon(aes(ymin = lower__, ymax = upper__, fill = treatment),
        alpha = 0.2, color = NA,
        position = position_dodge(width = 0.2)
    ) +
    facet_grid(~ relocation) +
    theme_classic(base_size = 14) +
    theme(
        panel.grid.major = element_line(color = "gray", linewidth = .1),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold"),
        axis.title = element_text(face = "bold"),
        axis.text = element_text(color = "black"),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    labs(
        x = "Information treatment",
        y = "Fairness rank (average)"
    ) +
    scale_color_brewer(palette = "Dark2") +
    scale_fill_brewer(palette = "Dark2")

p
```

```{r coeffs}
tables_rologit %>%
    filter(relocation_treatment != "All") %>%
    mutate(
        term = gsub("^info", "", term) %>%
            gsub("relocation_(.*)_ranking", "Alt (\\1)", .) %>%
            gsub("scale.*", "Asylum seekers (standard)", .) %>%
            dplyr::case_match(
                .,
                .default = .,
                "(Intercept):Alt (GDP)" ~ "Relocation by GDP",
                "(Intercept):Alt (population)" ~ "Relocation by population",
                "Asylum seekers (standard)" ~ "Asylum seekers (std.)",
                "No info:Alt (GDP)" ~ "No info x reloc. by GDP",
                "No info:Alt (population)" ~ "No info x reloc. by population",
                "Relative:Alt (GDP)" ~ "Info per capita x reloc. by GDP",
                "Relative:Alt (population)" ~ "Info per capita x reloc. by population",
            )
    ) %>%
    mutate(
        stars = dplyr::case_when(
            p.value < 0.01 ~ "***",
            p.value < 0.05 ~ "**",
            p.value < 0.1 ~ "*",
            TRUE ~ ""
        ),
        cis = sprintf("[%.1f,%.1f]", conf.low, conf.high),
        std.error = sprintf("(%.2f)", std.error),
        # estimate = sprintf("%.2f\\(^{%s}\\)", estimate, stars),
        estimate = sprintf("%.2f", estimate)
    ) %>%
    dplyr::select(
        term, estimate, std.error, cis, relocation_treatment
    ) %>%
    tidyr::pivot_longer(
        c(estimate, std.error, cis),
        names_to = "statistic"
    ) %>%
    tidyr::pivot_wider(
        names_from = relocation_treatment,
        values_fill = "",
    ) %>%
    dplyr::mutate(
        term = ifelse(row_number() == 1, term, ""),
        .by = term
    ) %>%
    dplyr::rename(Coefficient = term) %>%
    dplyr::select(-statistic) %>%
    kableExtra::kbl(
        booktabs = TRUE,
        caption = "Regression coefficients from rank-ordered logit on fairness rankings",
        align = "lcccc",
        escape = FALSE,
    ) %>%
    kableExtra::kable_styling(
        full_width = TRUE
    ) %>%
    kableExtra::column_spec(1, width = "15em") %>%
    kableExtra::footnote(
        "Standard errors in parenthesis, and 95% confidence intervals in square brackets."
    )
```

Figure \@ref(fig:rologit-ate) and Table \@ref(tab:coeffs) report the results of the rank-ordered logit model estimated separately for each information condition, thus all coefficients to vary across the treatment conditions. Across all groups, alternatives with proportional relocation, either by GDP or by populations, were consistently ranked as fairer, with positive and significant coefficients in each condition, again confirming earlier results. 

However, the strength of these effects varied: the control group showed the largest by-GDP and by-population effects (0.74 and 0.75, respectively), while these effects were smaller under the absolute and relative information conditions. The negative coefficients for asylum seekers indicate that schemes allocating more asylum seekers were viewed as less fair, though the magnitude of this effect differed significantly across groups. It was strongest in the absolute-information condition (−0.57, 95% CI: -0.62, -0.52), moderate in the relative-information condition (−0.40, 95% CI: -.45, -.35), and weakest in the control group (−0.13, 95% CI: -.17, -0.08). This pattern confirms that providing information, particularly absolute information, heightened sensitivity to the number of asylum seekers when evaluating fairness. 

<!-- When considering the size of this effect, our results show that the tendency to perceive as fairer the schemes that imply fewer asylum seekers, a “self-serving” bias, does not by itself fully offset the proportional relocation effects. Indeed, as Figure 3 shows, a one SD increase in the expected asylum seekers is necessary to completely offset the proportional allocation effect, implying that a sizeable deviation is needed to favour no relocation over a proportional scheme. -->

```{r rologit-ate, fig.cap = cap, fig.width = 5, fig.height = 3.5, out.width = "\\textwidth"}
short_cap <- "TBA"
cap <- "Estimates and 95% CIs from separate rank-ordered logit regressions on the probability of ranking an alternative relocation scheme as fairer, under each information treatment. $\\beta_{AS}^{\\tau}$ represents the effect of a SD change in expected asylum seekers on the probability of ranking an allocation scheme as fairer, under treatment $\\tau$. $\\alpha_{j}^{\\tau}$ represents the effect of a proportional allocation mechanism $j$ relative to the no relocation alternative (omitted), under treatment $\\tau$. This shows that the effects associated with a change in expected asylum seekers (AS) are stronger under absolute than relative information. A change in AS has a significant effect on fairness rankings even under no information, indicating some awareness of respondents beyond our intervention." # nolink

dodge <- 0.5

tables_rologit %>%
    filter(relocation_treatment != "All") %>%
    ggplot(
        aes(
            x = estimate,
            xmin = conf.low,
            xmax = conf.high,
            y = term,
            shape = reorder(relocation_treatment, estimate),
            color = reorder(relocation_treatment, estimate),
        )
    ) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
    geom_errorbar(width = 0.1, position = position_dodge(dodge)) +
    geom_point(position = position_dodge(dodge)) +
    scale_shape_discrete(
        name = expression("Treatment (" ~ tau ~ ")")
    ) +
    scale_color_brewer(
        name = expression("Treatment (" ~ tau ~ ")"),
        palette = "Set1"
    ) +
    scale_x_continuous(
        name = "Coefficient and 95% CIs",
        limits = c(-1, 1) * 0.85
    ) +
    scale_y_discrete(
        name = NULL,
        labels = c(
            "(Intercept):relocation_population_ranking" = expression(alpha[pop.]^tau),
            "(Intercept):relocation_GDP_ranking" = expression(alpha[GDP]^tau),
            "scale(asyl_skrs_rel)" = expression(beta[AS]^tau)
        )
    )
```

## Heterogenous effects

### Political orientation 

Figure \@ref(fig:political) shows that the effect of information on perceived fairness is strongly moderated by political orientation. The figure reports intercepts and slopes from the rank-ordered logit model, stratified by respondents’ political orientation (discretised into left, neutral, and right).^[
    Since we centered the expected number of asylum seekers for each alternative, the model's intercepts for the type of relocation (by GDP or by population) represent the average treatment effect on the probability of ranking the scheme as fairer than having no relocation at all.
] Across all groups, respondents assign a positive “premium” to relocation schemes relative to no relocation: intercepts are significantly above zero in all conditions. This premium is largest among left-leaning respondents, smaller among centrists, and weakest among right-leaning respondents. Intercepts are largely similar across information treatments.

By contrast, information substantially shapes sensitivity to the number of asylum seekers. In all models, alternatives with higher numbers of asylum seekers are associated with lower perceived fairness, but both absolute and relative information amplify this effect, especially among centrist and right-leaning respondents. The partisan divide is most pronounced under absolute information: right-leaning respondents react most negatively to higher numbers (−0.76), whereas left-leaning respondents are considerably less sensitive (−0.35), indicating a sharp ideological gap in fairness perceptions.

```{r political, fig.cap = cap, fig.width = 5, fig.height = 3.5, out.width = "\\textwidth"}
cap <- "Heterogeneous Treatment Effects by Political orientation. Coefficients and 95% confidence intervals from rank-ordered regression on the probability of ranking an alternative relocation shceme as fairer, stratified by the self-reported political orientation."

p_hetero_political <- tbl_coeffs_hetero_raw %>%
    filter(group_var == "political_right") %>%
    ggplot(
        aes(
            x = estimate,
            y = term,
            xmin = estimate - 1.96 * std.error,
            xmax = estimate + 1.96 * std.error,
            color = condition,
            shape = condition,
        )
    ) +
    geom_vline(xintercept = 0, color = "red") +
    geom_errorbar(width = 0.5, position = position_dodge(.5)) +
    geom_point(position = position_dodge(.5)) +
    facet_grid(group ~ .) +
    scale_shape_discrete(
        name = expression("Treat. (" ~ tau ~ ")"),
    ) +
    scale_color_brewer(
        name = expression("Treat. (" ~ tau ~ ")"),
        palette = "Set1"
    ) +
    scale_x_continuous(
        name = "Estimates and 95% CI"
    ) +
    scale_y_discrete(
        name = NULL,
        labels = c(
            "asyl_skrs_rel_scaled" = expression(beta[AS]^tau),
            "(Intercept):relocation_population_ranking" = expression(alpha[pop.]^tau),
            "(Intercept):relocation_GDP_ranking" = expression(alpha[GDP]^tau)
        )
    )

p_hetero_political
```


### Fair share 

Figure \@ref(fig:fair) illustrates the heteogeneity of the effects between individuals who reported the number of migrants in their own country as "fair" or "too low" vs those perceiving it as "too high". Both groups show higher perceived fairness for relocation schemes compared to no relocation, with all intercepts significantly positive. However, among respondents reporting that the current share is “fair or too low,” we do not detect a meaningful average treatment effect of framing: support is lowest under the Absolute condition, particularly for relocation by population (Estimate = 0.56, SE = 0.08) compared with GDP-based relocation (Estimate = 0.73, SE = 0.08). By contrast, in the group perceiving the share as “too high,” the Absolute framing significantly reduced support relative to Control for both GDP and population schemes (GDP: 0.29 vs. 0.61; Population: 0.38 vs. 0.65), with Relative framing falling in between and not significantly different from Control.

At the same time, for respondents reporting a “too high” share, we observe strong and significant heterogeneous effects of the expected number of asylum seekers on each relocation scheme. The negative impact of a one standard deviation increase in asylum seekers was largest under the Absolute condition (Estimate = -0.79, SE = 0.04), followed by the Relative condition (-0.56, SE = 0.04), and smallest in the Control group (-0.19, SE = 0.04). This corresponds to a difference of approximately 0.60 between Absolute and Control, substantially larger than the corresponding difference in the “fair or too low” group, which is 0.26.

```{r fair, fig.cap = cap}
cap <- "Heterogeneous Treatment Effects by Perceived Fairness of Migrants' Distribution in the EU. Coefficients and 95% confidence intervals from rank-ordered regression on the probability of ranking an alternative relocation shceme as fairer, stratified by whether respondents perceive the share of refugees in their country as 'too high' or not."

p_hetero_political %+%
    filter(tbl_coeffs_hetero_raw, group_var == "fair_share")
```

### Age

Figure \@ref(fig:age) illustrates the heterogeneity of the effects between younger and older respondents. Both age groups show higher support for relocation schemes compared to no relocation, with all intercepts significantly positive. However, among younger respondents, we do not detect a meaningful average treatment effect of information provision, which is instead notable for older respondents (45 years old and above). 

```{r age, fig.asp=1, fig.cap = cap}
cap <- "Heterogeneous Treatment Effects by Age. Coefficients and 95% confidence intervals from rank-ordered regression on the probability of ranking an alternative relocation shceme as fairer, stratified by the respondents' age."

p_hetero_political %+%
    filter(tbl_coeffs_hetero_raw, group_var == "age_cat")
```

### Konowledge of the Asylum System

Figure \@ref(fig:age) illustrates the heterogeneity of effects stratified by self-reported knowledge or awareness of the rules governing the EU asylum system. Remarkably, we do not observe significant differences between individuals with basic knowledge and those with more advanced understanding.

```{r knowledge, fig.cap = cap}
cap <- "Heterogeneous Treatment Effects by Knowledge of the Asylum System. Coefficients and 95% confidence intervals from rank-ordered regression on the probability of ranking an alternative relocation shceme as fairer, stratified by the self-reported knowledge or awareness of the rules governing the asylum system in the EU."

p_hetero_political %+%
    filter(tbl_coeffs_hetero_raw, group_var == "asylum_knowledge")
```

### Trust in the EU

Figure \@ref(fig:trust) illustrates the heterogeneity of effects stratified by individuals’ overall trust in the EU. We find that sensitivity to information is particularly pronounced among those with low levels of trust.

```{r trust, fig.cap = cap, out.width = "\\textwidth", fig.width = 5, fig.height=3.5}
cap <- "Heterogeneous Treatment Effects by Trust in the EU. Coefficients and 95% confidence intervals from rank-ordered regression on the probability of ranking an alternative relocation shceme as fairer, stratified by the overall trust in the EU. The original 0-10 scale was grouped into high, medium, and low categories."

p_hetero_political %+%
    filter(tbl_coeffs_hetero_raw, group_var == "trust_eu")
```


