```{r, include = FALSE}
fig_caption_smooth <- function(x) {
    sprintf(
        "Conditional average treatment effects by %s. Estimates and 95%% confidence intervals from a generalized additive model with regression splines, showing the relationship between %s and average fairness rankings, stratified by relocation mechanism and country being net sender or net receiver", # nolint
        x, x
    )
}
```

# Results

## Top-ranked Perceived Fairness of Relocation Systems

Respondents ranked three relocation mechanisms by perceived fairness. A clear majority of the sample (76%) ranked one of the proportional relocation mechanisms as fairest, with the GDP-based relocation receiving the highest share (41%), followed closely by population-based relocation (35%). Only 24% considered no relocation as the fairest option. Population-weighting of respondents by country of residence yields similar results, confirming the sample's representativeness, as shown in Figure \@ref(fig:relocation-weighted).

Figure \@ref(fig:toprank) illustrates how the average effect of information provision on fairness perceptions varies depending on whether countries are "net senders" or "net receivers" of applications under a proportional system. Among net sender countries, only 13% and 17% of respondents selected "No relocation" as the fairest option in the absolute and relative information groups, respectively, compared to 27% in the no-information group. Thus, information provision reduces the share of respondented ranking no relocation as fairest by about 10 percentage points. Conversely, among the net receiver countries, information provision increases perception of fairness for no relocation by about 10 percentage points. Because treatment was randomly assigned, these differences are consistent with causal treatment effects of information provision, with effects shifting sign between net sender and net receiver countries, consistent with a self-serving bias.

```{r toprank, fig.cap = cap, out.width="\\textwidth"}
knitr::include_graphics(
    here::here("output", "figures", "top_rank_by_cntry_type.png"),
    auto_pdf = TRUE
)

cap <- "Estimates and 95% CIs of the share of respondents ranking each relocation mechanism as the fairest (rank = 1) across information conditions: no information (Control), relative information, and absolute information about asylum applications implied under each relocation mechanism. Countries are classified as net senders (receivers) when asylum applications per 100,000 inhabitants exceed (fall below) the proportional-by-population relocation relative to a no-relocation benchmark." # nolint
```

Figure \@ref(fig:toprank-by-cntry) shows substantial cross-country heterogeneity. For instance, in Germany (a net receiver), 58% ranked some form of relocation as the fairest option, which is the lowest share among the selected countries, while in Greece (a net sender) the proportion was highest at 87%. Relocation by GDP was commonly perceived as the fairest in Bulgaria (53%), Greece (48%) and Spain (48%), but not in Germany (19%) or Sweden (27%). Views on relocation by population also varied: the share of respondents assigning it the top rank range from 24% in Poland to 45% in Italy.

## Average Treatment Effects on Fairness Rankings

Figure \@ref(fig:mean-rank) presents predicted mean rankings from a linear regression model, illustrating the average treatment effect on the perceived fairness for each relocation mechanism conditional on the country being net sender vs receiver. Ordinal regression models yield substantively similar results but are omitted for brevity. 

Under no information (Control group), net-receiver countries perceive “no relocation” as the least fair option, with a mean rank of 2.4 out of 3. However, they perceive “no relocation” increasingly *fairer* in the Relative and Absolute groups, with the largest effect observed under absolute information, where its mean rank goes from 2.4 to 2.1. By contrast, net sender countries perceive "no relocation" as increasingly *less fair* in the information treatments, for instance, increasing the ranking from 2.4 in the control to 2.6 under absolute information. Overall, these results are consistent with our hypotheses that individuals react more when information is presented in absolute than in relative terms.^[
    As a robustness test of the overall associations between fairness rankings and treatment assignment, we used separate Chi-squared tests within each country with Bonferroni correction for multiple testing. Even after applying Bonferroni correction, all the country-specific associations were statistically significant (p. < 0.01), confirming a robust treatment effect in most countries, as hypothesised.
]

```{r mean-rank, fig.cap = cap, out.width = "\\textwidth"}
knitr::include_graphics(
    here::here("output", "figures", "avg_rank.png"),
    auto_pdf = TRUE
)

cap <- paste(
    "Information provision and fairness rankings. Points show the expected fairness rankings (with 95\\% CI) conditional on the assigned information treatment and the country of residence being net sender or net receiver. Lower average ranks indicate higher perceived fairness. Countries are classified as net receivers if expected asylum applications are higher under relocation than under no relocation (based on GDP or population), and as net senders otherwise." # nolint
)
```

## The Role of Implied Asylum Applications

We next examine whether the expected number of asylum applications implied by each relocation mechanism influenced perceived fairness across treatment conditions. Figure \@ref(fig:implied-applications) presents fitted linear regressions of the average fairness ranking on the standardized number of implied asylum applications, interacted with the treatment indicators. A joint F-test indicates a statistically significant interaction between implied asylum applications and treatment assignment (F(2, 73.4) = 58.18, p < 0.001), suggesting that the relationship between implied asylum applications and perceived fairness differed across the three information conditions.

Figure \@ref(fig:implied-applications) further shows that perceived fairness declines as the expected number of implied asylum applications increases. This relationship is weakest in the No Information treatment, as indicated by the relatively flat slope, stronger in the Relative Information treatment, and strongest in the Absolute Information treatment. These findings suggest that providing information about the consequences of relocation mechanisms increased respondents' sensitivity to the asylum application levels implied by those mechanisms when evaluating their fairness, and the sensitivity is highest when such consequences are reported in absolute numbers.^[
    These results are robust to alternative specifications. Specifically, we obtained nearly identical results using a rank-ordered logit regression, which was discussed in a previous version of this paper.
]

```{r implied-applications, fig.cap = cap, out.width = "0.7\\textwidth"}
knitr::include_graphics(
    file.path("output/figures/avg_rank_asylum_applications_lm.png"),
    auto_pdf = TRUE
)

cap <- "Association between standardized asylum application rates and the perceived fairness of alternative relocation mechanisms across treatment conditions. The figure shows fitted linear regression lines relating the z-scored number of asylum applications implied by each relocation mechanism to its average perceived fairness ranking. The y-axis displays reversed average fairness rankings, such that mechanisms judged to be more fair appear higher on the axis. Shaded bands represent 95% confidence intervals around the fitted regression lines." # nolint
```

## Heterogenous effects

In this section, we examine whether the effects of information provision on perceived fairness vary systematically across respondent characteristics. Understanding such heterogeneity is important for assessing not only the average treatment effects, but also the conditions under which information is more or less persuasive. We therefore explore a range of theoretically relevant moderators, including political orientation, perceptions of current migration levels, age, knowledge of the EU asylum system, and trust in the EU. 

We formally test whether the inclusion of these interaction terms improves model fit using likelihood-ratio comparisons based on ANOVA tests between each pair of nested models. Table \@ref(tab:anova) in the Appendix presents the results of these tests. Overall, we find that the more flexible specifications with interaction terms significantly outperform their corresponding baseline models, providing statistical support for the presence of heterogeneous treatment effects. The figures below illustrate these heterogeneities in terms of conditional average treatment effects across the respective moderating variables.


### Political orientation 

Figure \@ref(fig:political) shows that the effect of (absolute) information on perceived fairness varies with respondents’ political orientation, measured on an 11-point left–right scale (0 = left, 10 = right). For the “no relocation” option, for instance, the difference in average rankings between the control and absolute information groups is smaller among left-leaning respondents (below 5) than among right-leaning respondents. Yet, the overall direction of these effects remains positive for net senders (no relocation is *less fair*) and negative for net receivers (no relocation is *fairer*). Thus, political leanings moderate the size of the information effects, but not the direction. A similar pattern is observed when comparing the control against relative information.

```{r political, fig.cap = cap, out.width = "\\textwidth"}
knitr::include_graphics(
    auto_pdf = TRUE,
    path = file.path(
        "output", "figures", "political_right.png"
    )
)
cap <- fig_caption_smooth("political orientation (left-right scale)")
```

It is worth noting that our measure of political orientation is from the European Social Survey (ESS) and has been widely applied in studies on voters' positioning in Europe. Nevertheless, this measure is not perfectly comparable across EU countries because the meaning of ‘left’, ‘neutral’ and ‘right’ can vary substantially depending on national party systems and migration discourses. Hence, our political orientation measure should be interpreted as a self-identified ideological placement rather than a harmonized cross-national construct. We return to the limitations of this measure in the Discussion.

### Fair share

Figure \@ref(fig:fair) shows how the effects of (absolute) information differ across respondents who perceive the number of migrants in their own country as “too low,” “fair,” or “too high.” The results indicate that information provision is most effective among individuals who believe migration levels are too high in their country, regardless of the country being net sender or net receiver.^[
    It is important to note that relatively few respondents fall into the “fair” or “too low” categories, which may limit statistical power for estimating conditional effects in these groups.
]

<!-- Both groups show higher perceived fairness for relocation schemes compared to no relocation, with all intercepts significantly positive. However, among respondents reporting that the current share is “fair or too low,” we do not detect a meaningful average treatment effect of framing: support is lowest under the Absolute condition, particularly for relocation by population (Estimate = 0.56, SE = 0.08) compared with GDP-based relocation (Estimate = 0.73, SE = 0.08). By contrast, in the group perceiving the share as “too high,” the Absolute framing significantly reduced support relative to Control for both GDP and population schemes (GDP: 0.29 vs. 0.61; Population: 0.38 vs. 0.65), with Relative framing falling in between and not significantly different from Control. -->

<!-- At the same time, for respondents reporting a “too high” share, we observe strong and significant heterogeneous effects of the expected number of asylum seekers on each relocation scheme. The negative impact of a one standard deviation increase in asylum seekers was largest under the Absolute condition (Estimate = -0.79, SE = 0.04), followed by the Relative condition (-0.56, SE = 0.04), and smallest in the Control group (-0.19, SE = 0.04). This corresponds to a difference of approximately 0.60 between Absolute and Control, substantially larger than the corresponding difference in the “fair or too low” group, which is 0.26. -->

```{r fair, fig.cap = cap, out.width = "\\textwidth"}
knitr::include_graphics(
    auto_pdf = TRUE,
    path = file.path("output", "figures", "fair_share.png")
)

cap <- fig_caption_smooth("perceived fairness of migrants' distribution in the EU")
```

### Age

Figure \@ref(fig:age) illustrates how the effects of information provision vary conditional on the age of the respondents. We observe larger conditional average treatment effects for older people, particularly the curves diverge for those aged 45 or higher. These results are further confirmed by linear regression with crossed dummies between treatment and age categories, showing statistically significant interactions. Thus, information provision seems to be more effective for older respondents.
<!-- However, among younger respondents, we do not detect a meaningful average treatment effect of information provision, which is instead notable for older respondents (45 years old and above).  -->

```{r age, fig.cap = cap, out.width = "\\textwidth"}
knitr::include_graphics(
    auto_pdf = TRUE,
    file.path(
        "output", "figures", "age.png"
    )
)
cap <- fig_caption_smooth("respondent's age (years)")
```

### Knowledge of the Asylum System

Figure \@ref(fig:knowledge) illustrates the heterogeneity of effects stratified by self-reported knowledge or awareness of the rules governing the EU asylum system. We observe little differences between individuals with basic knowledge and those with more advanced understanding.

```{r knowledge, fig.cap = cap, out.width = "\\textwidth"}
knitr::include_graphics(
    auto_pdf = TRUE,
    file.path(
        "output", "figures", "asylum_knowledge.png"
    )
)

cap <- fig_caption_smooth("knowledge of the EU asylum system (0 = no knowledge, 4 = expert)")
```


### Trust in the EU

Figure \@ref(fig:trust) illustrates the heterogeneity of effects stratified by individuals’ overall trust in the EU, as measured by an 11-item scale (0 = No trust, 10 = complete trust). We find that sensitivity to information is particularly pronounced among those with low levels of trust.

```{r trust, fig.cap = cap, out.width = "\\textwidth"}
knitr::include_graphics(
    auto_pdf = TRUE,
    path = file.path(
        "output", "figures", "trust_eu.png"
    )
)

cap <- fig_caption_smooth("trust in the EU (0 = low, 10 = high)")
```


