```{r methods, include = FALSE}
suppressMessages({
    library(dplyr)
    library(dplyr)
    library(knitr)
    library(tidyr)
    library(stringr)
    library(kableExtra)
})

path <- file.path(
    "data",
    "processed",
    "fair_survey_clean.rds"
)

ds <- readRDS(path)
message("Loaded data from ", path)

is_html_or_latex <- function() {
    knitr::is_html_output() || knitr::is_latex_output()
}

# ----------------------------------------------------
# Process survey data
# ----------------------------------------------------
ds <- ds %>%
    dplyr::mutate(
        relocation_treatment = relevel(factor(relocation_treatment), ref = "Control"),
        male = sex == "Male",
        educ_high = ISCED == "High",
        educ_mid = ISCED == "Mid",
        educ_low = ISCED == "Low",
        across(where(is.logical), as.numeric)
    )

# ----------------------------------------------------
# Eurostat averages
# ----------------------------------------------------
tbl_asylum_rel <- data.frame(
    country = c(
        "Germany", "Spain", "Greece", "Bulgaria",
        "France", "Sweden", "Italy", "Poland"
    ),
    no_relocation = c(313, 138, 397, 178, 151, 344, 128, 16),
    population = c(169, 169, 169, 169, 169, 169, 169, 169),
    gdp = c(219, 136, 95, 65, 184, 230, 158, 92)
)
```

# Methods and Data

## The survey 

A sample representative of the adult population aged 18 years and over in eight EU countries (Bulgaria, France, Germany, Greece, Italy, Poland, Spain and Sweden) was drawn from Ipsos online panel by means of stratified random probability sampling. The selected countries were chosen to ensure a balanced representation of the European Union's diversity, with particular attention to coverage across macro-regions (Northern, Southern, Eastern, and Western Europe). The selection also reflects variation in key structural characteristics, including economic conditions (GDP per capita), population size, and the share of foreign-born residents.

The sampling was stratified by age, gender and geographic region (NUTS 1). Pre-defined sub-sample sizes ("quotas") were based on official population statistics provided by Eurostat. The overall sample size of the project included 8,122 participants. The main fieldwork took place between 30 September 2024 and 21 October 2024. Details of the field work and survey design are available elsewhere [see @blasco2025fairness].

## Experimental design

The survey embededed an experiment testing how different types of information affected participants' ranking of the fairness of three relocation rules for asylum seekers across EU countries:^[
    The experimental design and pre-analysis plan were pre-registered within the AEA RCT Registry (AEARCTR-0014194). The Ethics Research Board of the JRC approved the experimental protocol.
]

- **No relocation** (the baseline): asylum seekers remain in the country where they first arrive;
- Allocation **proportional to each country's population**: relocations ensure equity with population as a proxy for capacity;
- Allocation **proportional to each country's GDP**: relocations ensure equity with GDP as a proxy for capacity.

Respondents were asked to rank these allocation rules from the fairest (rank = 1) to the least fair (rank = 3). Before they did so, we varied the format and amount of information available across three conditions: 

- **No information** (the control),
- **Absolute** information: the expected number of asylum applications under each relocation scheme (expressed in thousands),
- **Relative** information: the expected number of asylum applications under each relocation scheme per 100,000 citizens.

To illustrate the underlying relocation problem captured by our experiment, Table \@ref(tab:relocation) reports the expected asylum applications in each country under each relocation rule. These figures are based on national statistics about each country's population, GDP, and historical (2014-2023) first-time asylum applications from Eurostat.^[
    In this study, GDP and population are intended as proxies for a country's reception and processing capacity, consistent with existing EU allocation proposals and policy debates [@thielemann2018refugee]. These indicators also provide respondents with clear and easily interpretable signals of a country's size and wealth, which, as research shows, are commonly used when evaluating “fairness” in international sharing [@kleider2019politics]. Even so, respondents may interpret the proportionality by GDP or population in different ways (e.g., a proxy for housing capacity or labour market conditions), which may conflate the meaning of "capacity" and limit the interpretation of the results.
]

A few observations can be made. First, historical asylum application rates vary substantially across countries, ranging from 16 per 100,000 inhabitants in Poland to 397 per 100,000 in Greece. Second, proportional allocation systems would significantly alter the current distribution of asylum applications. For example, under a population-proportional allocation scheme, Poland would receive an additional 153 applications per 100,000 inhabitants, while Greece would "send" 228 applications per 100,000 inhabitants to other countries. We refer to countries in this position as “net receivers” or “net senders.”

Third, proportional allocation rules would generate pronounced cross-country differences depending on the rule being based on population or GDP. For instance, under a GDP-proportional allocation system, Poland would still be a net receiver, but the additional inflow would be considerably smaller, decreasing from 153 applications per 100,000 inhabitants under a population-based system to 76 per 100,000 under a GDP-based system.

```{r relocation, eval = is_html_or_latex()}
tbl_asylum_rel %>%
    dplyr::mutate(
        country = factor(
            country,
            levels = country[order(no_relocation, decreasing = TRUE)]
        ),
        d_pop = population - no_relocation,
        d_gdp = gdp - no_relocation
    ) %>%
    dplyr::arrange(
        dplyr::desc(no_relocation)
    ) %>%
    dplyr::transmute(
        Country = country,
        "No relocation" = no_relocation,
        "By population" = population,
        "By GDP" = gdp,
        `Δ Population` = d_pop,
        `Δ GDP` = d_gdp
    ) %>%
    kableExtra::kbl(
        caption = paste(
            "Expected asylum applications under alternative",
            "burden-sharing rules (per 100,000 inhabitants)."
        ),
        booktabs = TRUE,
        linesep = "",
        align = c("l", rep("r", 5)),
        escape = FALSE
    ) %>%
    kableExtra::kable_styling(
        latex_options = c("hold_position"),
        full_width = FALSE,
        position = "center",
        font_size = 10
    ) %>%
    kableExtra::row_spec(0, bold = TRUE) %>%
    kableExtra::add_header_above(
        c(" " = 1, "Levels" = 3, "Differences vs. no relocation" = 2),
        bold = TRUE
    ) %>%
    kableExtra::footnote(
        general = "Entries report expected asylum applications per 100,000 inhabitants.",
        threeparttable = TRUE,
        general_title = "Note:"
    )
```


Finally, the survey included several modules that asked respondents about their socio-demographics, perceptions of the EU asylum system, support for different migration policies, and other background questions. The full questionnaire is in the Appendix. A descriptive analysis of the responses is presented in the technical report by @blasco2025fairness. In our analysis, we included control variables such as trust or political affiliation, as these are associated with attitudes towards migration [e.g.,@canetti2016threatened;@mitchell2021social]. We also consider various socio-demographic factors, such as income and employment status, gender, age, and the parents' country of birth. Whether the respondent was born abroad may be relevant because foreigners may hold different opinions on migration issues than natives [@berlinschi2019migrants].

## Data 

Table \@ref(tab:assignment-summary) in the Appendix illustrates the random assignment to the three information conditions in each country and overall. Each treatment group has about one third of total respondents per country, reflecting the stratified randomisation design.

Table \@ref(tab:summary) illustrates the distribution of key pre-treatment characteristics, including sex, age, education, trust, and perceptions across the three treatment groups. On average, respondents were 50 years old (with 16 years SD), with about half (47%) identifying as male. For simplicity of exposition and comparability across countries, education was merged into three broad categories: high (ISCED 5-8; 32% of respondents), medium (ISCED 3-4; 48%), and low (ISCED 0-2; 19%). On measures of trust, respondents reported moderate levels of general trust in others (M = 4.5, SD = 2.7), trust in the EU (M = 4.3, SD = 2.7), and trust in government (M = 3.7, SD = 2.9). 

Knowledge of the EU asylum system averaged 2.0 (SD = 0.7) on a 1-4 scale, thus the majority expresses no or basic knowledge. Most respondents reported there were "too many" asylum seekers in their country, with a mean of 2.6 on 1-3 scale from 1 = too few and 3 = too many. Similarly, on average, respondents view an unbalanced distribution of asylum seekers in the EU, reporting an average score of 3.1 (SD = 2.4) on 0-10 scale for the question about evenness across the EU. Yet, respondents reported broad consensus on the support on the importance of burden sharing among countries, providing equal rights, equal treatment, and having an equal distribution of asylum seekers relatively high, with means ranging from 6.9 to 7.4 on 0-10 scales. 

Table \@ref(tab:summary) also reports mean differences between the control group and the other treatment groups, with the standardised difference in parenthesis (the difference divided by the pooled standard deviation). For all these variables, the standardised differences between control and other groups is small, suggesting the distributions overlap well across treatment groups.^[
    These differences were estimated using OLS controlling for country fixed effets, thus accounting for the stratified randomisation.
]

```{r summary, eval = is_html_or_latex()}
# -----
# 1. Compute SMD
# -----
result <- lapply(names(ds), function(x) {
    column <- ds[[x]]

    if (!is.numeric(column) || all(is.na(column))) {
        return(NULL)
    }

    formula <- reformulate(c("relocation_treatment", "country"), x)
    fit <- lm(formula, data = ds, contrasts = list(country = "contr.sum"))

    ## compute pooled SD
    group_sds <- tapply(column, ds$relocation_treatment, sd, na.rm = TRUE)

    broom::tidy(fit) |>
        dplyr::mutate(
            pooled_sd = sqrt(sum(group_sds^2) / length(group_sds)),
            smd = estimate / pooled_sd,
            variable = x
        )
})

result <- dplyr::bind_rows(result)

# -----
# 2. Build table
# -----
tbl_covariates <- result %>%
    filter(
        str_detect(term, "relocation_treatment"),
        !str_detect(variable, "weight|restart_count|^t[DQ]|^tIn"),
    ) %>%
    mutate(
        stat = sprintf("%.2f [%.2f]", estimate, smd)
    ) %>%
    select(variable, term, stat) %>%
    pivot_wider(names_from = term, values_from = stat) %>%
    mutate(
        variable = recode(variable,
            age = "Age (years)",
            male = "Male (%)",
            educ_high = "High education (%)",
            educ_mid = "Mid education (%)",
            educ_low = "Low education (%)",
            trust = "Trust others (0-10)",
            trust_eu = "Trust in EU (0-10)",
            trust_gov = "Trust in government (0-10)",
            political_right = "Political right (0-10)",
            share_legal_migrants = "Share legal migrants",
            asylum_knowledge = "Knowledge of asylum system (1-4)",
            asylum_fraud_detected = "Fraud detection ability (0-10)",
            asylum_decisions_objective = "Asylum decisions are objective (0-10)",
            asylum_distr_even = "Asylums in EU are even (0-10)",
            fair_share =  "Asylums in own country (1 = too few, 3 = too many)",
            burden_sharing_important = "Importance of burden sharing (0-10)",
            equal_distribution_important = "Importance of equal distribution (0-10)",
            equal_treatment_important =  "Importance of equal treatment (0-10)",
            equal_rights_important = "Importance of equal rights (0-10)",
            quick_processing_important = "Importance of quick process (0-10)",
            Duration = "Completion time (mins)",
            number_accepted_refugees = "Accepted refugees in own country",
            .default = variable
        ),
        group = case_when(
            variable %in% c(
                "Age (years)", "Male (%)",
                "High education (%)", "Mid education (%)", "Low education (%)"
            ) ~ "Sociodemographics",
            variable %in% c(
                "Trust others (0-10)", "Trust in EU (0-10)",
                "Trust in government (0-10)", "Political right (0-10)"
            ) ~ "Political attitudes",
            variable %in% c(
                "Knowledge of asylum system (1-4)",
                "Fraud detection ability (0-10)"
            ) ~ "Knowledge",
            variable %in% "Completion time (mins)" ~ "Survey administration",
            TRUE ~ "Other"
        )
    ) %>%
    arrange(desc(group)) %>% 
    mutate(
        variable = str_replace(variable, "Importance of", "Value of"),
    ) 

groups <- unique(tbl_covariates$group)

tbl_covariates %>%
    mutate(variable = gsub("_", " ", variable)) %>%
    select(
        Variable = variable,
        `Relative treatment` = contains("Relative"),
        `Absolute treatment` = contains("Absolute")
    ) %>% 
    kableExtra::kbl(
        booktabs = TRUE,
        align = c("l", "c", "c"),
        escape = TRUE,
        caption = paste(
            "Covariate balance across treatment arms.",
            "Mean differences with respect to the control group."
        )
    ) %>%
    kableExtra::kable_styling(
        full_width = FALSE, 
        position = "center"
    ) %>%
    kableExtra::pack_rows(groups[1],
        start_row = 1,
        end_row = sum(tbl_covariates$group %in% groups[1])
    ) %>%
    kableExtra::pack_rows(groups[2],
        start_row = sum(tbl_covariates$group %in% groups[1]) + 1,
        end_row = sum(tbl_covariates$group %in% groups[1:2])
    ) %>%
    kableExtra::pack_rows(groups[3],
        start_row = sum(tbl_covariates$group %in% groups[1:2]) + 1,
        end_row = sum(tbl_covariates$group %in% groups[1:3])
    ) %>% 
    kableExtra::pack_rows(groups[4],
        start_row = sum(tbl_covariates$group %in% groups[1:3]) + 1,
        end_row = nrow(tbl_covariates)
    ) %>% 
    kableExtra::footnote(
        general = paste(
            "Entries report OLS coefficients from regressions", 
            "of each covariate on treatment indicators and country fixed effects.",
            "Standardized mean differences (SMDs) are reported in brackets."
        ),
        threeparttable = TRUE,
        general_title = "Note:"
    )
```

<!-- As reported in Table 3, formal tests for covariate balance within each country confirm that baseline characteristics are comparable across groups, with p values from separate tests above conventional thresholds (p > 0.05 ). We observed some imbalance across treatment groups. In the sex distribution, for example, we observe relatively more women in the "No Info" group in Poland (61%) and more men in the ‘Relative info’ group in Greece (59%), which we will account for in the analysis. Overall, however, the randomisation was generally successful. -->