# Supporting Materials

## Regression model for the fairness rankings

We used a rank-ordered logit model [e.g., @hausman1987specifying] to estimate the effect of a change in the expected number of asylum seekers under a relocation scheme on the probability of ranking the scheme higher in the fairness ranking. This model allows probabilities to depend on the differences among all alternatives in a latent "fairness" variable. We assume the latent variable to be a function of the expected asylum seekers (scaled), $AS$, and we allow the coefficients to vary by treatment. This variable can be formulated as:
\[
    \mu_{ij}^{\tau} = \alpha_{j}^{\tau} + \beta_{j}^{\tau} \text{AS},
\]
for all $i$ and $j$ alternatives, with $\alpha_{j}^{\tau}$ and $\beta_{j}^{\tau}$ set to zero for an arbitrary alternative and an arbitrary treatment condition $\tau$. We selected the no-relocation scheme as the reference alternative, and the reference treatment group is the absolute-information group, so the model yields estimates of differences between control vs absolute and absolute vs relative information.

\clearpage 

## Additional Tables and Figures 

### Random assignment by country

```{r random-assignment}
tab <- readRDS("../output/tables/table_country_treatment.rds")
as.data.frame.matrix(addmargins(tab, FUN = list(All = sum), quiet = TRUE)) |>
    kableExtra::kbl(
        caption = "Respondents by Treatment Assignment, per Country",
        booktabs = TRUE,
        format.args = list(big.mark = ","),
        linesep = c(rep("", nrow(tab) - 1), "\\addlinespace")
    ) |>
    kableExtra::kable_classic(full_width = TRUE)
```

\clearpage 

## Top Ranked Relocation Mechanisms by Perceived Fairness

```{r relocation-weighted, fig.cap = cap, out.width="\\textwidth"}
cap <- "Distribution of top-ranked asylum relocation mechanisms by perceived fairness in weighted and unweighted samples. Weights are based on Eurostat population demographics (2025)." # nolint
knitr::include_graphics(
    here::here("output/figures/asylum-relocation-weighted-vs-unweighted.png"),
    auto_pdf = TRUE
)
```

\clearpage 

### Perceived Fairness by Country

```{r toprank-by-cntry, fig.cap = cap, out.width = "\\textwidth"}
knitr::include_graphics(
    here::here("output/figures/top_rank_by_cntry.png"),
    auto_pdf = TRUE
)

cap <- "Perceived fairness (average rank) by country and information condition" # nolint
```


### Anova Table for Heterogenous Treatment Effects 

```{r anova}
tab <- readRDS(
    here::here(
        "output", "tables", "anova_table.rds"
    )
)
tab |>
    dplyr::select(-`Interaction added`, -`Base model`) |>
    kableExtra::kbl(
        booktabs = TRUE,
        caption = "ANOVA: Models with vs. without treatment × moderator interactions"
    ) |>
    kableExtra::kable_classic() |>
    kableExtra::footnote(
        "ΔDf = diff. deg. of freedom; F = statistic; p = p-value; ΔR² = diff. R2",
        "Base model: rank ~ alt * treatment * country_type + {moderator}",
    )
```